QALY Comparisons - Energy Crisis Interventions - NoSupport Baseline

### 2023-11-14 minos/testing/QALY_comparison_energyCrises_diff.Rmd
Updated the way configs get the components for a current run. Now the components are read from a text file, so we only have to modify 1 file instead of several. Also updated some transition models to point to the correct MCS or PCS, and cleaned up some things in modules

>>>>

```{r}
base <- noSupport
base.name <- 'energyDownliftNoSupport'
int <- support
int.name <- 'energyDownlift'

combined <- rbind(base, int)

## now SF12 plots for comparison
p1 <- ggplot(combined, aes(x = year, y = SF_12_MCS, group = intervention, colour = intervention, fill = intervention)) +
  geom_smooth()
p2 <- ggplot(combined, aes(x = year, y = SF_12_PCS, group = intervention, colour = intervention, fill = intervention)) +
  geom_smooth()

print(p1)
print(p2)

combined.SF12 <- combined %>%
  select(run_id, year, intervention, SF_12_MCS, SF_12_PCS) %>%
  pivot_wider(names_from = 'intervention',
              values_from = c('SF_12_MCS', 'SF_12_PCS')) %>%
  mutate(MCS_diff = .data[[paste0('SF_12_MCS_', int.name)]] - .data[[paste0('SF_12_MCS_', base.name)]],
         PCS_diff = .data[[paste0('SF_12_PCS_', int.name)]] - .data[[paste0('SF_12_PCS_', base.name)]]) %>%
  select(run_id, year, MCS_diff, PCS_diff)

p3 <- ggplot(combined.SF12, aes(x = year, y = MCS_diff)) +
  geom_smooth() +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  labs(title = 'Change in SF_12_MCS', subtitle = paste0(int.name, ' vs ', base.name)) +
  xlab('Year') +
  ylab('Change in MCS')

p4 <- ggplot(combined.SF12, aes(x = year, y = PCS_diff)) +
  geom_smooth() +
  geom_hline(yintercept = 0, linetype = 'dashed') +
  labs(title = 'Change in SF_12_PCS', subtitle = paste0(int.name, ' vs ', base.name)) +
  xlab('Year') +
  ylab('Change in MCS')

print(p3)
print(p4)
